Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-21 paper/output/regressions/window_10y.tex
#25 implement baseline with 200y window

\begin{table}[htbp]
   \caption{\label{tab:window_100y} Differences in trends after switching, by switch type}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:                       & All construction & State       & Private & Public goods\\  
      Model:                                     & (1)              & (2)         & (3)     & (4)\\  
      \midrule
      \emph{Variables}\\
      Switch to another state                    & 0.07$^{*}$       & 0.004       & 0.02    & -0.05$^{*}$\\   
                                                 & (0.04)           & (0.03)      & (0.03)  & (0.03)\\   
      Switch to another state $\times$ Conquest  & -0.03            & -0.08$^{*}$ & -0.03   & -0.005\\   
                                                 & (0.04)           & (0.05)      & (0.04)  & (0.03)\\   
      Switch to another state $\times$ Other     & -0.03            & -0.01       & -0.04   & 0.03\\   
                                                 & (0.04)           & (0.04)      & (0.03)  & (0.03)\\   
      Switching indicator                        & 0.01             & 0.05$^{*}$  & 0.006   & -0.02\\   
                                                 & (0.03)           & (0.03)      & (0.02)  & (0.03)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                                       & Yes              & Yes         & Yes     & Yes\\  
      Period                                     & Yes              & Yes         & Yes     & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                               & 2,955            & 2,955       & 2,955   & 2,955\\  
      R$^2$                                      & 0.4287           & 0.4530      & 0.4802  & 0.4493\\  
      Within R$^2$                               & 0.0020           & 0.0046      & 0.0007  & 0.0017\\  
      \midrule \midrule

@@

   \par \raggedright 
   Note: Table presents results of estimation equation \eqref{eq:baseline}. The switch type "Succession" is omitted as the  reference category. Yearly data was aggregated into periods of 100 years. Observations are at the city-period  level. Dependent variables are indicators that take the value 1 if  construction activity of the respective type was recorded. Standard errors are  clustered at the city level. *, **, and *** denote significance on the 10 percent, 5 percent, and 1 percent  level, respectively.
\end{table}

>>>>

\begin{table}[htbp]
   \caption{\label{tab:window_10y} Differences in trends after switching, by switch type}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:                       & All construction & State   & Private               & Public goods\\  
      Model:                                     & (1)              & (2)     & (3)                   & (4)\\  
      \midrule
      \emph{Variables}\\
      Switch to another state                    & 0.01$^{*}$       & 0.003   & -0.004                & -0.008$^{**}$\\   
                                                 & (0.009)          & (0.004) & (0.003)               & (0.003)\\   
      Switch to another state $\times$ Conquest  & -0.008           & -0.01   & 0.003                 & 0.004\\   
                                                 & (0.01)           & (0.007) & (0.005)               & (0.005)\\   
      Switch to another state $\times$ Other     & -0.01            & -0.005  & 0.002                 & 0.01$^{**}$\\   
                                                 & (0.01)           & (0.005) & (0.004)               & (0.005)\\   
      Switching indicator                        & -0.03$^{***}$    & -0.004  & -0.005                & -0.010$^{**}$\\   
                                                 & (0.01)           & (0.005) & (0.004)               & (0.004)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                                       & Yes              & Yes     & Yes                   & Yes\\  
      Period                                     & Yes              & Yes     & Yes                   & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                               & 35,168           & 35,168  & 35,168                & 35,168\\  
      R$^2$                                      & 0.1770           & 0.0835  & 0.1278                & 0.0890\\  
      Within R$^2$                               & 0.0004           & 0.0001  & $8.13\times 10^{-5}$  & 0.0004\\  
      \midrule \midrule

@@

   \par \raggedright 
   Note: Table presents results of estimation equation \eqref{eq:baseline}. The switch type "Succession" is omitted as the  reference category. Yearly data was aggregated into periods of 10 years. Observations are at the city-period  level. Dependent variables are indicators that take the value 1 if  construction activity of the respective type was recorded. Standard errors are  clustered at the city level. *, **, and *** denote significance on the 10 percent, 5 percent, and 1 percent  level, respectively.
\end{table}

### 2023-06-21 paper/output/regressions/window_50y.tex
#25 implement baseline with 200y window

\begin{table}[htbp]
   \caption{\label{tab:window_10y} Differences in trends after switching, by switch type}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:                       & All construction & State   & Private               & Public goods\\  
      Model:                                     & (1)              & (2)     & (3)                   & (4)\\  
      \midrule
      \emph{Variables}\\
      Switch to another state                    & 0.01$^{*}$       & 0.003   & -0.004                & -0.008$^{**}$\\   
                                                 & (0.009)          & (0.004) & (0.003)               & (0.003)\\   
      Switch to another state $\times$ Conquest  & -0.008           & -0.01   & 0.003                 & 0.004\\   
                                                 & (0.01)           & (0.007) & (0.005)               & (0.005)\\   
      Switch to another state $\times$ Other     & -0.01            & -0.005  & 0.002                 & 0.01$^{**}$\\   
                                                 & (0.01)           & (0.005) & (0.004)               & (0.005)\\   
      Switching indicator                        & -0.03$^{***}$    & -0.004  & -0.005                & -0.010$^{**}$\\   
                                                 & (0.01)           & (0.005) & (0.004)               & (0.004)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                                       & Yes              & Yes     & Yes                   & Yes\\  
      Period                                     & Yes              & Yes     & Yes                   & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                               & 35,168           & 35,168  & 35,168                & 35,168\\  
      R$^2$                                      & 0.1770           & 0.0835  & 0.1278                & 0.0890\\  
      Within R$^2$                               & 0.0004           & 0.0001  & $8.13\times 10^{-5}$  & 0.0004\\  
      \midrule \midrule

@@

   \par \raggedright 
   Note: Table presents results of estimation equation \eqref{eq:baseline}. The switch type "Succession" is omitted as the  reference category. Yearly data was aggregated into periods of 10 years. Observations are at the city-period  level. Dependent variables are indicators that take the value 1 if  construction activity of the respective type was recorded. Standard errors are  clustered at the city level. *, **, and *** denote significance on the 10 percent, 5 percent, and 1 percent  level, respectively.
\end{table}

>>>>

\begin{table}[htbp]
   \caption{\label{tab:window_50y} Differences in trends after switching, by switch type}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:                       & All construction & State         & Private & Public goods\\  
      Model:                                     & (1)              & (2)           & (3)     & (4)\\  
      \midrule
      \emph{Variables}\\
      Switch to another state                    & 0.02             & 0.02          & 0.002   & -0.04$^{***}$\\   
                                                 & (0.02)           & (0.02)        & (0.01)  & (0.01)\\   
      Switch to another state $\times$ Conquest  & 0.04             & -0.07$^{***}$ & -0.005  & 0.02\\   
                                                 & (0.04)           & (0.03)        & (0.02)  & (0.02)\\   
      Switch to another state $\times$ Other     & 0.008            & -0.02         & 0.006   & 0.04$^{**}$\\   
                                                 & (0.03)           & (0.02)        & (0.01)  & (0.02)\\   
      Switching indicator                        & -0.01            & 0.007         & -0.005  & 0.0006\\   
                                                 & (0.02)           & (0.02)        & (0.01)  & (0.01)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                                       & Yes              & Yes           & Yes     & Yes\\  
      Period                                     & Yes              & Yes           & Yes     & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                               & 6,635            & 6,635         & 6,635   & 6,635\\  
      R$^2$                                      & 0.3553           & 0.2798        & 0.3257  & 0.2917\\  
      Within R$^2$                               & 0.0009           & 0.0012        & 0.0002  & 0.0011\\  
      \midrule \midrule

@@

   \par \raggedright 
   Note: Table presents results of estimation equation \eqref{eq:baseline}. The switch type "Succession" is omitted as the  reference category. Yearly data was aggregated into periods of 50 years. Observations are at the city-period  level. Dependent variables are indicators that take the value 1 if  construction activity of the respective type was recorded. Standard errors are  clustered at the city level. *, **, and *** denote significance on the 10 percent, 5 percent, and 1 percent  level, respectively.
\end{table}
